---
title: "scmeth Vignette"
author: "Divy S. Kangeyan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
Contents
-----------
1. Introduction

2. Installation

3. Input files

4. Usage

    4.1 Functions 
    
    4.2 Report
    
---------------------

    
1. Introduction
---------------------
<p style="text-align: justify;">
Though a small chemical change in the genome, DNA methylation has significant impact in several diseases, developmental processes and other bioligcal changes. Hence methylation data should be analyzed carefully to gain biological insights. That is the main purpose of this package. 
</p>

<p style="text-align: justify;">
This bioconductor package containes functions to do quality control and preprocessing analysis for methylation data. This package is especially customized to use the output from the firecloud implementation of methylation pipeline. However it still has function to generate bsseq objects with methylation information given the bedgraph file obtained from *methyldackel*. For now only human and mouse genomes are supported in this package but in the future we will expand to other organisms. In addition to individual functions **report** function in the **scmeth** provides all inclusive report with most of the functions in this package. If users prefer they can just use the **report** function to gain summary of their data.
</p>

2. Installation
---------------------
**scmeth** is available in bioconductor and can be downloads using the following commands
```{r, eval=FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite("scmeth")
```

3. Input files
---------------------
<p style="text-align: justify;">
Main input files that is used in most of the functions is an .rda file containing *bsseq* object. This can be obtained from the firecloud implementation of the methylation pipeline. However if the user has an output from *Methyldackel* as a bedgraph file then they can use the **createRDA** and **combineRDA** function to create the bsseq object. When the user has this bsseq object it should firt be loaded with the following command
</p>

```{r, eval=FALSE}
load('methylationData.rda')
```

<p style="text-align: justify;">
These bsseq objects are saved as *bs*, so the user can use the loaded bsseq object in the functions of the package. 
</p>


4. Usage
---------------------

4.1 Functions


4.2 Report
<p style="text-align: justify;">
A comprehensive quality control report can be generated in the package vis **report** function in this package. report function takes the bs object, the directory where the report shoudl be saved, organism that this data is obtained from, the genomic build. Follwing is an example of how to use the report function

</p>

```{r, eval=FALSE}
scmeth::report(bs, '~/Documents',"Mus musculus","mm10")
```




Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
